# Milestone One
Names: Owen Suelflow, Jacob Posner, Sam Anthony

## Topic:
Looking at historical price data on individual tickers to glean insight into how prices change.

## Broad Questions:
1. What indicators predict price the best?
2. When a stock has earnings (e.g. reports how they did in the previous quarter), how does that affect stock price?
3. How can we best predict when a stock will change trends (e.g. go from an up trend to a down trend)

## Reading in data

#### Setup

```{r, message=FALSE, error=FALSE}
library(tidyverse)
library(ggplot2)
```


We have historical price data on all stocks in the Nasdaq. Each stock has its own ticker (e.g. 'AAPL'), and each has its own csv file with price data.
```{r, message=FALSE, error=FALSE}
# Reading in price data for 'AAPL'
aapl <- read_csv("../data/nasdaq_prices/stocks/AAPL.csv")
```

```{r}
tail(aapl)
```

## Codebook

1. Date
- A `date` object that lists the date in "YYYY-MM-DD" format
2. Open
- A double that gives the opening price of the stock each day
3. High
- A double that gives the high price of the stock each day
4. Low
- A double that gives the low price of the stock each day
5. Close
- A double that gives the closing price of the stock each day
6. Adj Close
- A double that gives the adjusted closing price of the stock each day (we will not be using this)
7. Volume
- A double that gives the amount of shares traded of the stock each day.

## Next Steps

We can try to answer the first question: Which indicators predict price the best? An indicator is a technical analysis tool that uses price data to produce a numerical value that tells us some information about the price. Most indicators can be calculated from the data we have.

